Project Light

### 2015-09-02 paper/paper.tex
small headline change
structure of implementation chapter, add general implementation details

% --- Author Metadata here ---
\conferenceinfo{Sample Conferenve}{'15 Potsdam, Germany}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

@@

The mote on the other side measures $n$ light values using its light sensor.
The time between two measurements will probably not be equal to $T$, because the period length is unknown the mote at this point.
As long as \textit{bright} and \textit{dark} values are part of the $n$ measurements, the concrete time does not matter.
After reading $n$ values, the mote calculates reasonable numeric values for \textit{bright} and \textit{dark}.
For instance, this can be achieved by applying a \mbox{\textit{2-means}} algorithm (add reference to implementation).
After that, the mote is able to classify new light values.
In other words, it can read bits.

@@

With completion of the first two phases, the mote is now able to read data sent by the phone.
It learned a decision threshold for decoding the bits and the period length to read values at the right time.
Figure~\ref{fig:read_a_bit} shows how data can be read. 
However, the concrete implementation slightly differs from that figure, see (add reference to implementation).

@@

\begin{itemize}
	\item hamming code, crc32 checksum, when to read a bit (at the end of the period)
	\item Android app - functionality, flashlight, limitations
	\item contiki process - functionality, rtimer?, kmeans?, limitations
	\item driver wrapper to delay link layer initialization until key is initialized
\end{itemize}

@@

\section{Future Work}
\label{sec:future_work}

>>>>

% --- Author Metadata here ---
\conferenceinfo{Sample Conference}{'15 Potsdam, Germany}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

@@

The mote on the other side measures $n$ light values using its light sensor.
The time between two measurements will probably not be equal to $T$, because the period length is unknown to the mote at this point.
As long as \textit{bright} and \textit{dark} values are part of the $n$ measurements, the concrete time does not matter.
After reading $n$ values, the mote calculates reasonable numeric values for \textit{bright} and \textit{dark}.
For instance, this can be achieved by applying a \mbox{\textit{2-means}} algorithm (add reference to implementation).
After that, the mote is able to classify new light values.
In other words, it can read bits.

@@

With completion of the first two phases, the mote is now able to read data sent by the phone.
It learned a decision threshold for decoding the bits and the period length to read values at the right time.
Figure~\ref{fig:read_a_bit} shows how data can be read. 
However, the actual implementation slightly differs from that figure, see (add reference to implementation).

@@

Project Light consists of an Android app that creates and sends the key material and a Contiki process that runs on the sky mote and receives and validates it.
Both follow the aforementioned communication protocol very closely, but increase reliability and fail-safeness through the following design decisions.

All data that is being sent is encoded using a Hamming(8,4)-code so that two-bit errors can be detected and one-bit errors can be corrected.

The CRC32 is chosen as the checksum algorithm for the validation phase to avoid saving erroneous key material.
This could be caused by 3-or-more-bit errors that the Hamming-code failed to detect.

As the android timer that triggers the bit "emission" cannot be too early but in fact tends to be a little late (cite android real time paper), the time at which the mote reads a bit is not in the middle of a period as suggested by Figure~\ref{fig:read_a_bit}.
It is at the very end of a period to maximize error avoidance due to "timer-lateness".

\subsection{Android app}
\label{sub:android_app}

functionality, flashlight, limitations

\subsection{Mote}
\label{sub:mote}

\subsubsection{Contiki process}
\label{ssub:contiki_process}

functionality, rtimer?, kmeans?, limitations

\subsubsection{Contiki driver wrapper}
\label{ssub:contiki_driver_wrapper}

driver wrapper to delay link layer initialization until key is initialized

@@

\section{Conclusion and Future Work}
\label{sec:future_work}
